---
title: "p8105_hw5_ry2417"
author: "Ruiqi Yan"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d(option = "viridis")
scale_fill_discrete = scale_fill_viridis_d(option = "viridis")
```

## Problem 1

```{r}
homicide_df_raw <- 
  read_csv("data/homicide-data.csv", na = c("", "Unknown"))
```

There are `r homicide_df_raw %>% nrow()` cases of homicide with `r homicide_df_raw %>% ncol()` variables in this data. The variables are `r homicide_df_raw %>% colnames() %>% paste(collapse = ", ")`. There are `r homicide_df_raw %>% count(state) %>% nrow()` states and `r homicide_df_raw %>% count(city) %>% nrow()` cities. 

```{r}
homicide_df <- 
  homicide_df_raw %>% 
  mutate(
    city_state = str_c(city, str_to_upper(state),sep = ","),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "Tulsa,AL") 
```


```{r}
baltimore_df <-
  homicide_df %>% 
  filter(city_state == "Baltimore,MD")

baltimore_summary <-
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )
baltimore_test <-
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate across cities

First of all, write a function.

```{r}
prop_test_function = function(city_df){
  city_summary <- 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  city_test <- 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  return(city_test)
}

homicide_df %>% 
  filter(city_state == "Albuquerque,NM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities.

```{r}
results_df <-
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
  
```

Try to make a plot showing estimates and confidence intervals.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

summarizes within cities to obtain the total number of homicides and 
the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”)

```{r}
results_df_2 <- 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    num_homicide = n(),
    num_unsolved = sum(resolution == "unsolved")
  ) %>% 
  mutate(
    test_results = map2(num_unsolved, num_homicide, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

results_df_2 %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2


```{r}
list_file_names <- list.files("data/data", full.names = TRUE)

study_df <- 
  tibble(
    file_names = list_file_names
  ) %>% 
  mutate(
    observation_data = map(file_names, read_csv),
    id = str_extract(file_names, pattern = "[[:digit:]]+"),
    arm = str_sub(file_names, start = 11, end = 13)
  ) %>% 
  relocate(arm, id) %>% 
  unnest(observation_data) %>% 
  select(-file_names)
```

Some examples of the resulted data frame shown as 
`r study_df %>% head(10) %>% knitr::kable()`

A spaghetti plot showing observations on each subject over time

```{r}
study_df %>% 
  pivot_longer(cols = starts_with("week_"),
               names_to = "week",
               names_prefix = "week_",
               values_to = "observations") %>% 
  mutate(arm_id = str_c(arm, id, sep = "_"),
         week = as.numeric(week)) %>% 
  ggplot(aes(x = week, y = observations, group = arm_id, color = arm, label = arm_id)) +
  geom_line() +
  labs(
    title = "Observations of Each Subject Over Time(Control vs. Experiment)",
    caption = "Data from a Longitudinal Study"
  ) +
  scale_color_discrete(labels = c("control", "experiment"))
```

The observations of experimental arm is increasingly higher than the observations of control arm over time.
The difference of observations between control arm and experimental arm increases over time.\


## Problem 3

```{r, echo = TRUE}
set.seed(10)

iris_with_missing <- iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r, echo = TRUE}
fill_in_missing <- function(input_vector) {
  if (is.numeric(input_vector)) {
    output_vector <- ifelse(is.na(input_vector), 
                          mean(input_vector, na.rm = TRUE),
                          input_vector)
  } 
  if(is.character(input_vector)){
    output_vector <- ifelse(is.na(input_vector), 
                          "virginica",
                          input_vector)
  }
  
  return(output_vector)
}

iris_no_missing <-
  iris_with_missing %>% 
  map_df(fill_in_missing)

iris_no_missing %>% 
  head(10) %>% 
  knitr::kable()
```

